Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-18 analysis/study2.qmd
study2 html

```{r}

data <- rbind(data, pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive"))

>>>>

```{r}
# names(df10)[str_detect(names(df10), "PI_Alive")]
# names(df12)[str_detect(names(df12), "PI_Alive")]
# names(df13)[str_detect(names(df13), "PI_Alive")]

data <- rbind(
  data, 
  pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive", unequalrange=TRUE))
